# Courses {#courses}

<!-- See the [FAQ page](http://www.twintownstriathlon.org.au/?page_id=28){target="_blank"} for more info and the  [official description](http://www.twintownstriathlon.org.au/?page_id=3809){target="_blank"} of the full course. -->

```{r course-map,include=FALSE}

dummy <- lapply(list.files("R", full.names = TRUE), source)

# icon example https://github.com/rstudio/leaflet/issues/691

list_icons <- awesomeIconList(
  swimmer = makeAwesomeIcon(text = fa("person-swimming"),markerColor = "blue"),
  traffic = makeAwesomeIcon(text = fa("traffic-light"), markerColor = "black"),
  marshall = makeAwesomeIcon(text = fa("circle-user"), markerColor = "pink"),
  timer = makeAwesomeIcon(text = fa("stopwatch"), markerColor = "black"),
  circle = makeAwesomeIcon(text = fa("circle-xmark"), markerColor = "black", iconColor = "yellow")
)

unpack_points <- function(gpx_list, ord_name = c("lat","lon")[1]) {
  
  as.numeric(unlist(unname(lapply(gpx_list$gpx$trk$trkseg, function(x) attr(x, ord_name)))))
}

import_gpx <- function(path_gpx) {
  gpx_list <- as_list(xml2::read_xml(path_gpx))
  
  lats <- unpack_points(gpx_list, "lat")
  lons <- unpack_points(gpx_list, "lon")

  return(st_linestring(x = matrix(c(lons, lats),ncol=2),dim = "XY"))
}


dt_courses <- data.table(course = c("full","full","full (old)","full (old)","int (old)","int (old)"),
                                    part = c("ride","run","ride","run","ride","run"),
                         # dist_km = c(16.7,4.4,NA,NA,NA,NA),
                         path_gpx = c("data_provided/courses/Twinnies full proposed.gpx",
                                      "data_provided/courses/Reconning.gpx",
                                      "data_provided/courses/TT_Tri_Ride.gpx",
                                      "data_provided/courses/TT_Tri_Run.gpx",
                                      "data_provided/courses/TT_Tri_Intermediate_Ride.gpx",
                                      "data_provided/courses/TT_Tri_Intermediate_Run.gpx"))

dt_courses[, row_id := seq(.N)]
dt_courses[, sf_poly := list(list(import_gpx(path_gpx))), by = row_id]
dt_courses[, c("xmin", "ymin","xmax","ymax") := as.list(st_bbox(sf_poly[[1]])), by = row_id]



sf_trans <- st_polygon(list(matrix(
  c(153.53715076025483, -28.214527587458402, 
         153.53732204033093, -28.214552769875205, 
         153.5372821355182, -28.214802763001195, 
         153.53710607076877,-28.214777784964596, 
         153.53715076025483, -28.214527587458402),
  ncol=2,byrow = TRUE)))

dt_courses_range <- dt_courses[, .(xmin = min(xmin),
               ymin = min(ymin),
               xmax = max(xmax),
               ymax = max(ymax))]

dt_markers_new <- data.table(lat = c(-28.213376212245354, 
                                 -28.231228,-28.209872829666857, -28.19393845224043,
                                 -28.194949373861867),
                         lng = c(153.5226650096654,
                                 153.526104, 153.52372975721073, 153.53884997902225,
                                 153.54222891317784),
                         popup = c(rep("Traffic lights",1),
                                   "Marshall: Fraser Dr upper roundabout at Altitude Blvd",
                                   "Marshall: Fraser Dr lower roundabout at Stradbroke Dr",
                                   "Marshall: Corner of Oxley St & Cunningham St",
                                   "Timer"
                         ),
                         icon = c(rep("traffic",1),
                                  rep("marshall",3),
                                  "timer"))

dt_markers <- data.table(lat = c(-28.214021, -28.214762,
                                 -28.231228, -28.214127, -28.227960, -28.216583,
                                 -28.214749),
                         lng = c(153.540331, 153.525837,
                                 153.526104, 153.528090, 153.538349, 153.541749,
                                 153.537454),
                         popup = c(rep("Traffic lights",2),
                                   "Marshall: Fraser Dr Roundabout",
                                   "Marshall: Woodlands Dr Roundabout",
                                   "Marshall: Lochlomond Dr Roundabout",
                                   "Marshall: Toolona Ave Roundabout",
                                   "Timer"
                                   ),
                         icon = c(rep("traffic",2),
                                  rep("marshall",4),
                                  "timer"))



```

### New Courses

New courses based at TRAC Tweed Heads South

- [Full (Proposed)](#course-full-new)
- Intermediate TBC

### Old Courses

- [Old Courses](#course-old)


## Full (New Proposed) {#course-full-new}

The new courses are based at TRAC Tweed Heads South

Scroll down for [Course Map](#map-full-new) and [Bike Course Directions](#course-directions-full-new)

Distances are similar to the previous course:

- Swim 500m (20x25m laps)
- Ride 16.7km
- Run 4.4km

Traffic lights: 1 set on Fraser Dr heading south

Marshalls: 3 shown in pink icons on the map:

- Corner of Oxley St & Cunningham St
- Fraser Dr lower roundabout at Stradbroke Dr
- Fraser Dr upper roundabout at Altitude Blvd

### Course Map {#map-full-new}

```{r}
leaflet(width = "100%", height = 400) %>% 
  addTiles(group = "Detailed") %>% 
  addProviderTiles(providers$CartoDB.Positron, group = "Simple") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Satellite") %>% 
  fitBounds(lng1 = dt_courses_range$xmin,
            lng2 =dt_courses_range$xmax,
            lat1 = dt_courses_range$ymin,
            lat2 = dt_courses_range$ymax) %>% 
  # Add general markers
  addAwesomeMarkers(data = dt_markers_new,
                    lng = ~lng, lat =~lat,
                    icon = ~list_icons[icon],popup = ~popup, group = "Info") %>% 
  
  
# Add swimming marker -28.215316, 
  addAwesomeMarkers(lat = -28.195599589008136, lng = 153.5421932591716,
                    icon = list_icons["swimmer"], # fixed list, can't accept hex
                    popup = "20x25m laps",
                   group = "Swim") %>%

  # Add courses
  addPolylines(data = dt_courses[course=="full" & part=="ride"]$sf_poly[[1]], color = tri_cols$ride, group = "Ride") %>% 
  addPolylines(data = dt_courses[course=="full" & part=="run"]$sf_poly[[1]], color = tri_cols$run, group = "Run") %>% 

  addFullscreenControl() %>% 
  addScaleBar(position = "bottomleft") %>% 
  addLegend(position = "topleft",colors = c(tri_cols$ride, tri_cols$run),labels = c("Ride","Run")) %>%
  addLayersControl(position = "topleft",baseGroups = c("Simple","Detailed", "Satellite"),
                   overlayGroups = c("Swim","Ride","Run", "Info"),
                   options = layersControlOptions(collapsed = TRUE)) %>% 
  # hideGroup(c("Full (old)","Intermediate (old)", "Info (old)"))
  widgetframe::frameWidget(options = frameOptions(allowfullscreen = TRUE))
```

### Bike Course Directions {#course-directions-full-new}

- Start from TRAC Tweed Heads South
- Left into Heffron Street
- Right into Oxley Street
- Left into Cunningham Street
- Right into Sullivan Street
- Left into Dry Dock Road
- Left into Fraser Drive
- Continue all the way up Fraser Drive to the roundabout at Altitude Blvd, go around roundabout to continue back down (north) Fraser Drive
- Left into Botanical Circuit
- Left into Leisure Drive
- Left into Fraser Drive
- Left into Kirkwood Road which becomes Philp Parade
- Left into Dry Dock Road
- Right into Sullivan Street
- Left into Cunningham Street
- Right into Oxley Street
- Left into Heffron Street to return to TRAC Tweed Heads South


## Old {#course-old}

Courses based at Club Banora Oasis Pools


```{r}
leaflet(width = "100%", height = 400) %>% 
  addTiles(group = "Detailed") %>% 
  addProviderTiles(providers$CartoDB.Positron, group = "Simple") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Satellite") %>% 
  fitBounds(lng1 = dt_courses_range$xmin,
            lng2 =dt_courses_range$xmax,
            lat1 = dt_courses_range$ymin,
            lat2 = dt_courses_range$ymax) %>% 
  # Add general markers
  addAwesomeMarkers(data = dt_markers,
                    lng = ~lng, lat =~lat,
                    icon = ~list_icons[icon],popup = ~popup, group = "Info (old)") %>% 
  
  # Add transition
  addPolygons(data = sf_trans,color = "black", fillColor = "black",
              label = "T",labelOptions = labelOptions(noHide = TRUE,
                                                      direction = "center",
                                                      textOnly = TRUE,textsize = "20px"),
              group = "Info") %>% 
  
# Add swimming marker
  addAwesomeMarkers(lat = -28.215370, lng = 153.537490,
                    icon = list_icons["swimmer"], # fixed list, can't accept hex
                    popup = "10x50m laps",
                   group = "Full") %>%
  addAwesomeMarkers(lat = -28.215370, lng = 153.537490,
                    icon = list_icons["swimmer"], # fixed list, can't accept hex
                    popup = "6x50m laps",
                   group = "Intermediate") %>%
  # intermediate turn around
  addAwesomeMarkers(lat = -28.217697, lng = 153.541171,
                    icon = list_icons["circle"], # fixed list, can't accept hex
                    popup = "Run: Turn around at painted<br>yellow X on road",
                   group = "Intermediate") %>%
  # Add courses
  addPolylines(data = dt_courses[course=="full (old)" & part=="ride"]$sf_poly[[1]], color = tri_cols$ride, group = "Full") %>% 
  addPolylines(data = dt_courses[course=="full (old)" & part=="run"]$sf_poly[[1]], color = tri_cols$run, group = "Full") %>% 
  addPolylines(data = dt_courses[course=="int (old)" & part=="ride"]$sf_poly[[1]], color = tri_cols$ride, group = "Intermediate",popup = "2 laps") %>% 
  addPolylines(data = dt_courses[course=="int (old)" & part=="run"]$sf_poly[[1]], color = tri_cols$run, group = "Intermediate") %>% 
  addFullscreenControl() %>% 
  addLegend(position = "topleft",colors = c(tri_cols$ride, tri_cols$run),labels = c("Ride","Run")) %>%
  addLayersControl(position = "topleft",baseGroups = c("Simple","Detailed", "Satellite"),
                   overlayGroups = c("Full","Intermediate","Info"),
                   options = layersControlOptions(collapsed = TRUE)) %>% 
  addScaleBar(position = "bottomleft") %>% 
  hideGroup(c("Intermediate")) %>% 
  widgetframe::frameWidget(options = frameOptions(allowfullscreen = TRUE))
```

