# (PART) Season

# Schedule

```{r}

dt_season_show <- dt_season[course=='full', .(`Race #` = race_number,
                            Date = date_ymd,
                            `Event type` = race_type,
                            cancelled,
                            cancelled_reason,
                            have_results)]

dt_season_show[(cancelled), Note:= paste0("Cancelled due to ", cancelled_reason)]
dt_season_show[!(cancelled) & !(have_results), Note := "webscorer data not available"]
dt_season_show[is.na(Note), Note := ""]

knitr::kable(dt_season_show[, .(`Race #`,
                                Date,
                                `Event type`,
                                Note
                                )])
```

# Best Times - Full

The best valid times for each competitor are ranked in the plot and table below.

Disclaimer: These results are based on webscorer data but are completely unofficial. `r if(some_weeks_missing_full) paste0("Results are not available for the following weeks: ", paste0(weeks_missing_full, collapse= ", "))`.


```{r}
n_athletes <- nrow(dt_all_long[course=="full" & (isPB_overall) & part=="Swim"])

htmltools::tags$iframe(
  src = "plot_record_full.html", 
  scrolling = "no", 
  seamless = "seamless",
  frameBorder = "0",
  width = "100%",
  height = 150 + 16*n_athletes
)
```


Season records are show in gold, split PBs are shown in green, and invalid times in grey.


```{r}
htmltools::tags$iframe(
  src = "tab_overall_full.html", 
  scrolling = "yes", 
  #seamless = "seamless",
  frameBorder = "0",
  width = "100%",
  height = "700"
)
```

# Best Times - Intermediate

The best valid times for each competitor are ranked in the plot and table below.


Disclaimer: These results are based on webscorer data but are completely unofficial. `r if(some_weeks_missing_full) paste0("Results are not available for the following weeks: ", paste0(weeks_missing_int, collapse= ", "))`.


```{r}
n_athletes <- nrow(dt_all_long[course=="int" & (isPB_overall) & part=="Swim"])

htmltools::tags$iframe(
  src = "plot_record_int.html", 
  scrolling = "no", 
  seamless = "seamless",
  frameBorder = "0",
  width = "100%",
  height = 150 + 16*n_athletes
)
```

Season records are show in gold, split PBs are shown in pink, and invalid times in grey.

```{r}
htmltools::tags$iframe(
  src = "tab_overall_int.html", 
  scrolling = "yes", 
  #seamless = "seamless",
  frameBorder = "0",
  width = "100%",
  height = "700"
)
```
