--- 
title: "Twinnies Times"
author: "Created by Josh Horsley, updated `r as.integer(format(Sys.time(),'%d'))` `r format(Sys.time(),'%b %Y')`"
site: bookdown::bookdown_site
documentclass: book
link-citations: yes
description: "Twinnies Times"
---

# Home

```{r prep, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.height = 6, fig.width = 7)

dummy <- lapply(list.files("R", full.names = TRUE), source)

dt_season <- readRDS("data_derived/dt_season.rds")
dt_all_long <- readRDS("data_derived/dt_all_long.rds")

season_lowest <- min(dt_season$season)

```

This is an unofficial collection of [TwinTowns Triathlon Club](http://www.twintownstriathlon.org.au){target="_blank"} race results based on the [club's webscorer page](https://www.webscorer.com/33755){target="_blank"}.

See results by:

- Race ([eg 5 Feb 2022](#r-2022-02-05))
- [Competitor](#athletes)
- Season participation and records ([eg 2021-2022](#season-2021-2022))
- [Race entries](#participation-total-all)

Results are available from the `r season_lowest` season onwards:


```{r season-table}

dt_season_tab <- dt_season[, .(Seasons =unique(season))]

dt_season_tab[, Seasons := paste0('<a href="season-',Seasons, '.html#',Seasons,'">',Seasons,'</a>')]

DT::datatable(dt_season_tab, rownames = FALSE,escape = FALSE,
              options = list(ordering = FALSE,
                             paging = FALSE,
                             dom = 't'))

```



# Participation {#participation-total-all}

```{r}
n_entries_all <- nrow(dt_all_long[(started) & part == "Swim"])
n_athletes <- length(unique(dt_all_long[(started) & part == "Swim"]$Name))
```

There have been `r prettyNum(n_entries_all, big.mark = ",")` entries by `r prettyNum(n_athletes, big.mark = ",")` competitors since the `r season_lowest` season


```{r part_hist-all}
plotly_part_hist(dt_all_long, do_all = TRUE)
```


```{r part-total-table-all}
table_part_total(do_all = TRUE)

```

